### 2011-09-14 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.
Thesis: in progress

TODO remind what these parameters mean

\subsubsection{Effects on performance}

TODO, we are expecting no influence

\subsubsection{Effects on the ID set}

@@

@@

>>>>

TODO remind what these parameters mean, remind that because these are weights, only their ratio matters. We have thus a 1-dimensional problem. However, for simplicity's sake we will use 25 combinations of alpha and beta and normalize them only during evaluation.

TODO we do not expect any changes in performance and will limit the inquiry to different ID sets produced under different settings

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & all official test data sets \\
  Iterations        & 1 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $\{0.1, 0.25, 0.5, 0.75, 1\} \times \{0.1, 0.25, 0.5, 0.75, 1\}$ \\ % TODO this is not the best way to write it
  \hline
\end{tabular}
\bigskip
\end{center}

\begin{algorithm}
\caption{Various values of $\alpha$ and $\beta$}
\label{listing-experiment-various-betas}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$\alpha \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
  \FOR{$\beta \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
    \FOR{$file \in $ official test data}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1, alpha = \alpha, beta = \beta), IH = \emptyset\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

Following data sets have the same optimal ID sets regardless of the setting of $\alpha$ and $\beta$: \dataset{100-1000}, \dataset{MSH}, \dataset{NTH}, \dataset{XMA-c}, \dataset{XMA-p}.

TODO remaining datasets showed various dependencies on alpha and beta, because this question is not central to our interest we shall mention only 2 examples

TODO in 100-200 we have a clear boundary, in OVA1 (representative of OVAs in general) we have unclear boundary

\subsubsection{Results for \dataset{100-200}}

2 different sets (too long to list here), very nice boundary when we normalize alpha and beta

\subsubsection{Results for \dataset{OVA1}}

TODO found 2 ID sets:

\begin{table}
  \caption{Different ID sets found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1}
  \centering
  \begin{tabular}{c || c}
    ID set 1: element@attribute & ID set 2: element@attribute \\
    \hline
    \texttt{aff@fa} & \texttt{aff@fa} \\
    \texttt{com@ty} & \texttt{com@ty} \\
    \texttt{cre@da} & \texttt{cre@da} \\
    \texttt{cri@te} & \texttt{cri@te} \\
    \texttt{cve@st} & \texttt{cve@st} \\
    \texttt{\textbf{def@id}} & \texttt{\textbf{def@cl}} \\ % TODO again, my bold typewriter does not work
    \texttt{fil@co} & \texttt{fil@co} \\
    \texttt{mod@da} & \texttt{mod@da} \\
    \texttt{ova@xs} & \texttt{ova@xs} \\
    \texttt{pat@op} & \texttt{pat@op} \\
    \texttt{sof@op} & \texttt{sof@op} \\
    \texttt{sta@da} & \texttt{sta@da} \\
    \texttt{sub@or} & \texttt{sub@or} \\
    \texttt{sbt@te} & \texttt{sbt@te} \\
  \end{tabular}
\end{table}

\begin{table}
  \caption{Effect of $\alpha$, $\beta$ on ID set found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-effect}
  \centering
  \begin{tabular}{c | c  c  c  c  c}
    $\alpha$ \textbackslash $\beta$ & 0.1 & 0.25 & 0.5 & 0.75 & 1 \\
    \hline
    0.1  & 1 & 2 & 2 & 1 & 1 \\
    0.25 & 2 & 2 & 2 & 1 & 2 \\
    0.5  & 2 & 1 & 1 & 1 & 2 \\
    0.75 & 1 & 2 & 1 & 2 & 1 \\
    1    & 1 & 2 & 1 & 1 & 2 \\
  \end{tabular}
\end{table}

TODO linear - we have more than 1 combination that has the same ratio (explain what this ratio is)

\begin{table}
  \caption{Effect of $\alpha$\ ratio on ID set found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-ratio-effect}
  \centering
  \begin{tabular}{c | c || c |  c}
    $\alpha$ ratio & ID set & $\alpha$ ratio & ID set \\
    \hline
    0,091	& 1 & 0,500	& 2 \\
    0,118	& 1 & 0,500	& 2 \\
    0,167	& 2 & 0,571	& 1 \\
    0,200	& 2 & 0,600	& 1 \\
    0,250	& 1 & 0,667	& 1 \\
    0,286	& 2 & 0,667	& 1 \\
    0,333	& 2 & 0,714	& 2 \\
    0,333	& 2 & 0,750	& 2 \\
    0,400	& 1 & 0,800	& 2 \\
    0,429	& 1 & 0,833	& 2 \\
    0,500	& 1 & 0,882	& 1 \\
    0,500	& 2 & 0,909	& 1 \\
    0,500	& 1 &       &   \\
  \end{tabular}
\end{table}

TODO no clear separation, same ratio producing different sets? Randomness in GLPK input.

\subsubsection{Interpretation}

TODO we just note that there are differences, but will not investigate any further

TODO artificial data always has only one attribute

@@

TODO play around with ratio in Mutation, but perhaps this is not enough - in that case move this after chained IHs, and try to tweak the best one by fiddling around with ratios.

@@

TODO we will try 3 different scenarios, see which performs the best on the data and then try to tweak it a bit.
